An Improved ANS Transaction Template

### 2018-01-26 paper.tex
more changes

\subsection{Relevant Cases}
\subsubsection{Reference Case}
The reference case corresponds to the most ideal cascade design--utilizing all the 5060
centrifuges available within JCPOA to produce an enriched product at $>90\%$ of U-235,
stripping the tail product up to 0.28 $\%$ from a feed of natural uranium.
The design cascade in this case, includes 4 stripping stages, and 38 enriching
stages. The Feed/Product/Tail (F/P/T) assays are respectively
0.0071/0.903/0.0028.
%maybe include some cascade shape figures?

@@

\subsubsection{Case 2}
Case 2 also limited to 30 cascades in the scenario (the maximum allowable under
the JCPOA agreement), but this time each level of cascade are designed to get
feed with the previous level product and to have 4 stripping stages and 10
enriching stages. The configuration of the different level of cascade can be
found in table \ref{tab:cascadelvl}. The different cascades don't have the same
geometry: the number of centrifuges per stage depends on their own design and
varies slightly from a level to another.
%we haven't defined a level

@@

\bottomrule
\end{tabular}
  \caption{Summary of the different properties of the different level of cascade.}
  \label{tab:cascadelvl}
\end{table}

\subsection{Level optimisation}
A last round of optimisation if then ran in order to limit the number of cascade
level to the amount of level required produce HEU, and then to populate the
different level with a total of 30 cascades in order to maximize the HEU
production rate.

\section{Results}
\subsection{Enrichment}
\subsubsection{Without tail recycling}
Despite the reconfiguration of each level occurring in the second case, the case
1 is way more effective to produce HEU than case 1.Indeed as observed on Figure
\ref{fig:assay_c1_nc} and \ref{fig:assay_c2_nc}, the first case is able to
produce an uranium product enrich at $98\%$ while the second case is only able
to reach an enrichment of $88.3\%$.

@@

Because the cut value at each stage is unchanged it artificially produces over
enriched tails when feed with higher enriched materials compared to a cascade
feed with the same feed assay but with a cascade designed for it.  The effective
cut values for each cascade can be computed as :

@@

\bottomrule
\end{tabular}
  \caption{Cascade effective $\theta$ as a function of the cascade level and the
  case considered.}
  \label{tab:cascade_theta}
\end{table}
As illustrated on Table \ref{tab:cascade_theta} the effective cut of the
different level increase up to $0.54$ for the fifth stage on case 2. The high
effective cut value increase the product production rate but decrease the
enrichment ratio.

@@

\subsubsection{Case 1}
As shows on Figure \ref{ }, without tails recycling, the number of cascade level
required to enrich the uranium up to $90\%$ are respectively 5 for the
first case considered. Recycling the tails, allow to reduce the number of
enrichment levels required to enrich natural uranium up to a high enrich level
to 3.

This bump in enrichment can easily be explained, as the cascade does not have the
same number of stages, there is less stripping enrichment work, than enriching
work. That is to say that even work in an ideal case (where the stripping work of a
stage is the exact inverse of the enrich work), with an cascade with less
stripping stage than enriching stage will produce tail with a higher enrichment
than the feed of the previous level of

>>>>

\subsection{Relevant Cases}
\subsubsection{Reference Case}
The reference case corresponds to the most ideal cascade design--utilizing all of the 5060
centrifuges available within JCPOA to produce an enriched product at $>90\%$ of U-235,
stripping the tail product up to 0.28 $\%$ from a feed of natural uranium.
The design cascade in this case, includes 4 stripping stages, and 38 enriching
stages. The Feed/Product/Tail (F/P/T) assays are respectively
0.0071/0.903/0.0028.
%maybe include some cascade shape figures?

@@

\subsubsection{Case 2} Case 2 also limited to 30 cascades in the scenario (the
maximum allowable under the JCPOA agreement), but this time each level of
cascades are designed to take feed from the previous level's product. Each
cascade has 4 stripping stages and 10 enriching stages. The configuration of
cascade levels can be found in table \ref{tab:cascadelvl}. Unlike case 1, the
organization of centrifuges varies from level to level. Each level is re-optimized
to have the most efficient number of centrifuges in each stage, although the total number
of stages remains constant. T

 %we haven't defined a level

@@

\bottomrule
\end{tabular}
  \caption{Summary of cascade properties for each level}
  \label{tab:cascadelvl}
\end{table}

\subsection{Level optimization}
A last round of optimization if then ran in order to limit the number of cascade
level to the amount of level required produce HEU, and then to populate the
different level with a total of 30 cascades in order to maximize the HEU
production rate.

\section{Results}
\subsection{Enrichment}
\subsubsection{Without tail recycling}
Despite the reconfiguration of each level occurring in the second case, the case
1 is notably more effective in producing HEU than case 1. Indeed, as observed in Figure
\ref{fig:assay_c1_nc} and \ref{fig:assay_c2_nc}, the first case is able to
produce an uranium product enrich at $98\%$ while the second case is only able
to reach an enrichment of $88.3\%$ with the same number of levels.

@@

Because the cut value $\theta_i$ at each stage is unchanged, case 2 artificially
produces over-enriched tails when fed with higher enriched materials compared
to a cascade feed with the same feed assay but with a cascade designed for it.

% ^ the above paragraph is confusing but I don't understand it enough to fix it

The effective cut values for each cascade can be computed as :

@@

\bottomrule \end{tabular} \caption{Cascade effective $\theta$ as a function of
the cascade level and the case considered.} \label{tab:cascade_theta}
\end{table} As illustrated in Table \ref{tab:cascade_theta}, the effective cut
of each level increases up to $0.54$ for the fifth stage for case 2. The high
effective cut value increase the product production rate but decrease the
enrichment ratio.

@@

\subsubsection{Case 1}
As shows on Figure \ref{ }, without tails recycling, the number of cascade levels
required to enrich uranium up to $90\%$ is 5 for the
first case considered. Recycling the tails allows for a reduction in the number of
enrichment levels down to only 3.

This bump in enrichment can easily be explained, as the cascade does not have
the same number of stages, less work is spent on stripping as opposed to
enriching. Even compared to an ideal case, where the stripping
work of a stage is the exact inverse of the enriching work, a cascade with
less stripping stages will produce tails with a higher
enrichment than the feed of the previous level of

%Did you commit in the middle of a sentence or did you forget to finish?
